---
title: "Coding Kata"
output: html_notebook
---


A coding kata is a short exercise to help practice programming skills in short bursts.

Get started programming in R using these katas below.

Your best resources to help you solve these challenges will be Google, StackOverflow and the official R documentation.


# Kata #0 

## Opposite number

Very simple, given a number, find its opposite.

Examples:<br/>
1: -1 <br/>
14: -14 <br/>
-34: 34 <br/>
But can you do it in 1 line of code and without any conditionals?

Try solving this challenge by modifying the code block below.

```{r}
opposite <- function(number) {
  # Add your code here
  # Make sure to keep these lines indented
}
```

Tests for Kata #0: <br/>
The code blocks below should execute properly once you have written the code above.


```{r}
# Test Case 1: opposite(1)
print('Expected output: -1')
print(paste('Your function outputs ', toString(opposite(1))))
```

```{r}
# Test Case 2: opposite(-10)
print('Expected output: 10')
print(paste('Your function outputs ', toString(opposite(-10))))
```

```{r}
# Test Case 2: opposite(392)
print('Expected output: -392')
print(paste('Your function outputs ', toString(opposite(392))))
```

# Kata #1 

## Find Smallest Integer in the Vector 

Very simple, given a vector of integers, find the smallest number in it.

Given [34, 15, 88, 2], your solution will return 2.<br/> Given [34, -345, -1, 100], your solution will return -345. <br/>You can assume, for the purpose of this kata, that the supplied array will not be empty.

Try solving this challenge by modifying the code block below.

```{r}
find_smallest_int <- function(vec) {
  # Add your code here
  # Make sure to keep these lines indented
}
```

Tests for Kata #1
The code blocks below should execute properly once you have written the code above.

```{r}
# Test Case 1: 
a <- c(78, 56, 232, 12, 11, 43)
print('Expected output: 11')
print(paste('Your function outputs: ', toString(find_smallest_int(a))))
```
```{r}
# Test Case 2: 
a <- c(78, 56, -2, 12, 8, -33)
print('Expected output: -33')
print(paste('Your function outputs: ', toString(find_smallest_int(a))))
```
```{r}
# Test Case 3: 
a <- c(0, 1-2**64, 2**64)
print('Expected output: -18446744073709551616')
print(paste('Your function outputs: ', toString(find_smallest_int(a))))
```



# Kata #2

## Even or Odd
Create a function that takes an integer as an argument and returns "Even" for even numbers or "Odd" for odd numbers.

Code
Try solving this challenge by modifying the code block below.

```{r}
even_or_odd <- function(number) {
  # Add your code here
  # Make sure to keep these lines indented
}
```

Tests for Kata #2
The code blocks below should execute properly once you have written the code above.

```{r}
# Test Case 1: even_or_odd(2)
print('Expected output: Even')
print(paste('Your function outputs:', even_or_odd(2)))
```

```{r}
# Test Case 2: even_or_odd(7)
print('Expected output: Odd')
print(paste('Your function outputs:', even_or_odd(7)))
```

```{r}
# Test Case 3: even_or_odd(0)
print('Expected output: Even')
print(paste('Your function outputs:', even_or_odd(0)))
```

```{r}
# Test Case 4: even_or_odd(1)
print('Expected output: Odd')
print(paste('Your function outputs:', even_or_odd(1)))
```


# Kata #3

## String Repeat
Write a function called repeatStr which repeats the given string string exactly n times.
e.g:<br/>
repeatStr(6, "I") // "IIIIII"<br/>
repeatStr(5, "Hello") // "HelloHelloHelloHelloHello"<br/>

Try solving this challenge by modifying the code block below.

```{r}
repeat_str <- function(n, str) {
  # Add your code here
  # Make sure to keep these lines indented
}
```

Tests for Kata #3
The code blocks below should execute properly once you have written the code above.

```{r}
# Test Case 1: repeat_str(4, "a")
print('Expected output: aaaa')
print(paste('Your function outputs:', repeat_str(4, "a")))
```

```{r}
# Test Case 2: repeat_str(3, "hello")
print('Expected output: hellohellohello')
print(paste('Your function outputs:', repeat_str(3, "hello")))
```

```{r}
# Test Case 3: repeat_str(2, "abc")
print('Expected output: abcabc')
print(paste('Your function outputs:', repeat_str(2, "abc")))
```

# Kata #4

## Century From Year
Introduction The first century spans from the year 1 up to and including the year 100, The second - from the year 101 up to and including the year 200, etc.<br/>

Task Given a year, return the century it is in.<br/>

Input, Output Examples<br/>

century(1705)  # returns 18<br/>
century(1900)  # returns 19<br/>
century(1601)  # returns 17<br/>
century(2000)  # returns 20<br/>

Try solving this challenge by modifying the code below.<br/>

```{r}
centuryFromYear <- function(year) {
  # Add your code here
  # Make sure to keep these lines indented
}
```

Tests for Kata #4
The code blocks below should execute properly once you have written the code above.

```{r}
# Test Case 1: century(1705)
print('Expected output: 18')
print(paste('Your function outputs:', centuryFromYear(1705)))
```

```{r}
# Test Case 2: century(1900)
print('Expected output: 19')
print(paste('Your function outputs:', centuryFromYear(1900)))
```

```{r}
# Test Case 3: century(1601)
print('Expected output: 17')
print(paste('Your function outputs:', centuryFromYear(1601)))
```

```{r}
# Test Case 4: century(2000)
print('Expected output: 20')
print(paste('Your function outputs:', centuryFromYear(2000)))
```








